---
name: Jessica
surname: Gorzo
position: "Data Scientist"
pronouns: she/her
address: "Cellular Tracking Technologies"
www: avianecologist.com
twitter: setophaga
github: dendroica
linkedin: gorzo
date: "`r format(Sys.time(), '%B %Y')`"
output: (function (..., latex_engine = "xelatex") {; template <- ("awesome-cv_mod.tex"); vitae:::set_entry_formats(vitae:::awesome_cv_entries); vitae:::copy_supporting_files("awesomecv"); vitae::cv_document(..., template = template, latex_engine = latex_engine, keep_tex = TRUE)})
 #MIGHT HAVE TO SPECIFY PATH TO TEMPLATE
   # vitae::awesomecv:
#    page_total: true
  #vitae::cv_document:
  #  latex_engine: xelatex # Specify so it uses this instead of pdflatex
   # keep_tex: TRUE # Keep tex file in-between runs
  #  template: awesome-cv_mod.tex 
csl: apa-single-spaced_mod.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Recent Experience

```{r consulting}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Research associate", "Conservation Science Global, Inc.", "Remote", "Mar. 2024 - Present",
  list("Data wrangling and ecological analysis", "Working on a variety of projects to complete grant goals and produce required deliverables"),
  "Data scientist", "Cellular Tracking Technologies LLC", "Rio Grande, NJ", "Jul. 2020 - Present", 
    list("Develop methodology to estimate locations from radio and Bluetooth signals from wildlife telemetry devices",
         "Manage data pipelines and processes that deliver and display data via web interfaces"
    ),
  "Researcher", "Natural Resources Research Institute", "Duluth, MN", "Aug. 2016 - Jun. 2020", "Landscape Ecologist") %>% 
  detailed_entries(role, dates, company, loc, details) #%>%
   #knitr::knit_print()
```

## Contractor

```{r consult}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  
  "Marsh Bird Survey Technician", "New Jersey Dept. of Environmental Protection", "Tuckahoe, NJ", "Summer 2021, 2024", 
    list("Worked as a contractor to survey sensitive and endangered noctural avian species via boat transects", "Solely by-ear bird identification required for night surveys"
    ),
  "Co-Founder", "On the Wing Scientific Consulting LLC", "Remote", "Jul. 2018 - Present", 
    list("Data science consulting projects including spatio-temporal modeling", 
         "Create tools for improving workflows")) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "B.S. Biological Sciences", "2004-08", "Virginia Tech", "Blacksburg, VA",
  "M.S. Wildlife & Fisheries Biology", "2009-11", "Clemson University", "Clemson, SC",
  "Ph.D. Wildlife Ecology", "2012-16", "University of Wisconsin", "Madison, WI"
) %>%
  detailed_entries(Degree, Year, Institution, Where)
```
# Thesis & Dissertation
```{r}
bibliography_entries("mypubs.bib") %>% filter(type=="thesis")
```

# Peer-Reviewed Publications

```{r}
bibliography_entries("mypubs.bib") %>% filter(type=="article-journal")
```

# Conference Presentations
```{r}
bibliography_entries("mypubs.bib")  %>% filter(type=="paper-conference")
```

# Technical Reports
```{r}
bibliography_entries("mypubs.bib")  %>% filter(type=="report")
```

# Contributions  
StellaR: http://www.r-gis.net/stellar/

Updated code for Supplement 1. R Script in 2016 for the publication: Jackson, M. M., Turner, M. G., Pearson, S. M., & Ives, A. R. (2012). Seeing the forest and the trees: multilevel models reveal both species and community patterns. Ecosphere, 3(9), 1-16. https://figshare.com/articles/dataset/Supplement_1_R_script_and_input_data_file_for_creating_multilevel_models_using_the_forest_herb_data_set_described_in_the_main_text_/3563784?file=5637069

Contributed “Raptors and songbirds” (8.4.5.1) pp.565-566 in Jodice, P. G. R., Tavano, J., Mackin, W., & Michel, J. (2013). South Atlantic information resources: data search and literature synthesis. US Department of the Interior, Bureau of Ocean Energy Management, regulation, and enforcement, Gulf of Mexico OCS region, 475, 587

# Teaching
## Selected Invited Seminars
Gorzo, J.M. "Career Perspective: From Wildlife to Data Science." Stockton University (remote) 4/18/24  
Gorzo, J.M. "Networks and Connectivity in Landscape Ecology" University of Minnesota-Duluth, 2020  
Gorzo, J.M. "Introduction to Birding & Community Science" University of Wisconsin-Stevens Point, 2016  

```{r include=FALSE}
# Outreach, Service & Fundraising
#* Birding field guide (paid and volunteer) for various festivals (2015-2023)
#* World Series of Birding: Participant in Carbon Footprint Challenge (2015, 2021)
```
