---
name: Jessica
surname: Gorzo
position: "Research Associate"
pronouns: she/her
address: "Cellular Tracking Technologies, Erma, NJ"
www: avianecologist.com
twitter: setophaga
github: dendroica
linkedin: gorzo
date: "`r format(Sys.time(), '%B %Y')`"
output: (function (..., theme = "banking", latex_engine = "xelatex") {; theme <- match.arg(theme); template <- ("Gorzo_CVmod.tex"); vitae:::set_entry_formats(vitae:::moderncv_cv_entries); vitae:::copy_supporting_files("moderncv"); vitae::cv_document(..., pandoc_vars = list(theme = theme), template = template, latex_engine = latex_engine, keep_tex = TRUE)})
  #vitae::awesomecv
   # theme: banking
  #  keep_tex: TRUE
    #page_total: FALSE
  #vitae::cv_document:
   # latex_engine: xelatex # can't use for latexcv
   # template: moderncv.tex 
csl: apa-single-spaced_mod.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Recent Experience

```{r consulting}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Research associate", "Conservation Science Global, Inc.", "Remote", "Mar. 2024 - Present",
  list("Data wrangling and ecological analysis", "Working on a variety of projects to complete grant goals and produce deliverables"),
  "Data scientist", "Cellular Tracking Technologies LLC", "Rio Grande, NJ", "Jul. 2020 - Present", 
    list("Develop methodology to estimate locations from radio and Bluetooth signals",
         "Manage data pipelines and processes that deliver and display data via web interfaces"
    ),
  "Landscape Ecologist", "Natural Resources Research Institute", "Duluth, MN", "Aug. 2016 - Jun. 2020", "Researcher 5 (University of Minnesota - NRRI internal job title designation)") %>% 
  detailed_entries(role, dates, company, loc, details) #%>%
   #knitr::knit_print()
```

## Contractor

```{r consult}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  
  "Marsh Bird Survey Technician", "New Jersey Dept. of Environmental Protection", "Tuckahoe, NJ", "Summer 2021, 2024", 
    list("Worked as a contractor to survey sensitive and endangered noctural avian species via boat transects", "Solely by-ear bird identification required for night surveys"
    ),
  "Co-Founder", "On the Wing Scientific Consulting LLC", "Remote", "Jul. 2018 - Present", 
    list("Data science consulting projects including spatio-temporal modeling", 
         "Create tools for improving workflows")) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~details,
  "B.S. Biological Sciences", "2004-08", "Virginia Tech", "Blacksburg, VA", "Minors: Physics, Astronomy",
  "M.S. Wildlife & Fisheries Biology", "2009-11", "Clemson University", "Clemson, SC", "Minor: Experimental Statistics",
  "Ph.D. Wildlife Ecology", "2012-16", "University of Wisconsin", "Madison, WI", "Minor: distributed (required)"
) %>%
  detailed_entries(Degree, Year, Institution, Where, details)
```
# Thesis & Dissertation
```{r}
bibliography_entries("mypubs.bib") %>% filter(type=="thesis")
```

# Peer-Reviewed Publications

```{r}
bibliography_entries("mypubs.bib") %>% filter(type=="article-journal")
```

# Conference Presentations
```{r}
bibliography_entries("mypubs.bib")  %>% filter(type=="paper-conference")
```
# Technical Reports
```{r}
bibliography_entries("mypubs.bib")  %>% filter(type=="report")
```

# Contributions  
* StellaR: http://www.r-gis.net/stellar/

* Updated code for Supplement 1. R Script in 2016 for the publication: Jackson, M. M., Turner, M. G., Pearson, S. M., & Ives, A. R. (2012). Seeing the forest and the trees: multilevel models reveal both species and community patterns. Ecosphere, 3(9), 1-16. https://figshare.com/articles/dataset/Supplement_1_R_script_and_input_data_file_for_creating_multilevel_models_using_the_forest_herb_data_set_described_in_the_main_text_/3563784?file=5637069

* Contributed “Raptors and songbirds” (8.4.5.1) pp.565-566 in Jodice, P. G. R., Tavano, J., Mackin, W., & Michel, J. (2013). South Atlantic information resources: data search and literature synthesis. US Department of the Interior, Bureau of Ocean Energy Management, regulation, and enforcement, Gulf of Mexico OCS region, 475, 587

# Teaching
## Guest Lectures
```{r}
tribble(
  ~ what, ~ when, ~ with, ~where,
  "Career Perspective: From Wildlife to Data Science", "4/18/2024", "DSSA 5102: Data Gathering & Warehousing", "Stockton University",
  "Networks and Connectivity in Landscape Ecology", "2020", "Landscape Ecology","University of Minnesota-Duluth",
  "Introduction to Birding and Community Science", "2016", "WLDL 450/650: Human Dimensions in Wildlife","University of Wisconsin-Stevens Point"
) %>%
  detailed_entries(what, when, with, where, .protect = TRUE)
```

## Teaching Assistant  
```{r}
tribble(
  ~ what, ~when, ~with,
  "Forestry Practicum ('Summer Camp')", "2012, 2014", " Kemp Natural Resource Station",
  "Introduction to Astronomy Lab (2 Sections)", "2008", "Virginia Tech"
) %>%
  brief_entries(what, when, with)
```

## Short Course & Workshop Instructor  
```{r}
tribble(
  ~ what, ~when, ~with,
  "BIOSC 730: Wolves and Society", "2013", "Clemson University",
  "Introduction to Astronomy", "Fall 2007", "Elderhostel"
) %>%
  brief_entries(what, when, with)
```

# Outreach, Service & Fundraising
* Birding field guide (paid or volunteer) for various festivals
    * Cape May Fall Festival, Cape May Bird Observatory/NJ Audubon (2023-2024)
    * Cape May Spring Festival, Cape May Bird Observatory/NJ Audubon (2024)
    * Sax-Zim Bog Birding Festival (2014 - 2019)
* World Series of Birding: Participant in Carbon Footprint Challenge
    * 2015: tied for 1st
    * 2021: 2nd place in social/physical distance COVID-19 modified rules
* Great Wisconsin Birdathon Participant (2013, 2016)
* BRRRRDathon (Team Overall Winner, Record Setter Jan. 2013)  

## Television  
Expeditions – air date Oct 17 2010  
Guest appearance, season 4, Episode 7: “The ACE Basin – A Conservation Miracle”  
Discussed painted bunting habitat requirements, threats and conservation needs  
(Listing and TV show description:  
http://www.clemson.edu/public/expeditions/episode_guide/season_4.html )  

## Radio
Your Day – air date Aug 30 2010  
(Segment start 45:50 http://cufan.clemson.edu/psaradiopod/YDPodcast/YD100830.mp3 )  

## Academic
**Ad hoc reviewer**: Journal of Arid Environments, Landscape & Urban Planning, Landscape Ecology, PLOS ONE, Wilson Ornithological Society, Biological Conservation, Avian Conservation & Ecology  
**Professional Memberships**: Phi Kappa Phi Honors Society (inducted 2010), American Ornithological Society, US-International Association for Landscape Ecology

# Awards & Honors  
2015 Travel Award, American Ornithologist's Union/Cooper Ornithological Society Conference  
2011 Outstanding Service to the Clemson Experimental Forest  
Dean’s List (undergraduate)  

```{r include=FALSE}
# Certifications  
#Hunter’s Safety Certificate, Conservation Leaders of Tomorrow Workshop GA 2010  
#Certificate of Boating Safety Education, Maryland Department of Natural Resources  
#Coffee College, Virginia Tech  
```
