---
name: Jessica
surname: Gorzo
position: "Data Scientist"
pronouns: she/her
address: "Cellular Tracking Technologies"
www: avianecologist.com
twitter: setophaga
github: dendroica
linkedin: gorzo
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::cv_document:
    latex_engine: xelatex # Specify so it uses this instead of pdflatex
    keep_tex: TRUE # Keep tex file in-between runs
    template: mycv_public_mod.tex 
csl: apa-single-spaced_mod.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Recent Experience

```{r consulting}
library(tibble)
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Data scientist", "Cellular Tracking Technologies", "Rio Grande, NJ", "Jul. 2020 - Present", 
    list("Develop methodology to estimate locations from radio and Bluetooth signals from wildlife telemetry devices",
         "Manage data pipelines and processes that deliver and display data via web interfaces"
    ),
  "Co-Founder", "On the Wing Scientific Consulting LLC", "Remote", "Jul. 2018 - Present", 
    list("Data science consulting projects including spatio-temporal modeling", 
         "Create tools for improving workflows"),
  "Researcher", "Natural Resources Research Institute", "Duluth, MN", "Aug. 2016 - Jun. 2020", "Landscape Ecologist") %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "B.S. Biological Sciences", "2004-08", "Virginia Tech", "Blacksburg, VA",
  "M.S. Wildlife & Fisheries Biology", "2009-11", "Clemson University", "Clemson, SC",
  "Ph.D. Wildlife Ecology", "2012-16", "University of Wisconsin", "Madison, WI"
) %>%
  detailed_entries(Degree, Year, Institution, Where)
```
# Thesis & Dissertation
```{r}
library(dplyr)
bibliography_entries("mypubs.bib") %>% filter(type=="thesis")
```

# Peer-Reviewed Publications

```{r}
library(dplyr)
bibliography_entries("mypubs.bib") %>% filter(type=="article-journal")
```

# Conference Presentations
```{r}
library(dplyr)
bibliography_entries("mypubs.bib")  %>% filter(type=="paper-conference")
```

# Technical Reports
```{r}
library(dplyr)
bibliography_entries("mypubs.bib")  %>% filter(type=="report")
```

# Contributions  
StellaR: http://www.r-gis.net/stellar/

Updated code for Supplement 1. R Script in 2016 for the publication: Jackson, M. M., Turner, M. G., Pearson, S. M., & Ives, A. R. (2012). Seeing the forest and the trees: multilevel models reveal both species and community patterns. Ecosphere, 3(9), 1-16. https://figshare.com/articles/dataset/Supplement_1_R_script_and_input_data_file_for_creating_multilevel_models_using_the_forest_herb_data_set_described_in_the_main_text_/3563784?file=5637069

Contributed “Raptors and songbirds” (8.4.5.1) pp.565-566 in Jodice, P. G. R., Tavano, J., Mackin, W., & Michel, J. (2013). South Atlantic information resources: data search and literature synthesis. US Department of the Interior, Bureau of Ocean Energy Management, regulation, and enforcement, Gulf of Mexico OCS region, 475, 587

# Outreach, Service & Fundraising
* Birding field guide (paid and volunteer) for various festivals (2015-2023)
* World Series of Birding: Participant in Carbon Footprint Challenge (2015, 2021)
